An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
make pilot study table look nicer

\usepackage{listings}
\usepackage{hyperref}
\renewcommand{\topfraction}{0.9}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.84}

@@

\begin{table*}
\centering
\begin{tabular}{| l | l | l | l |}
\hline
Institution & Course & Language & Enrollment\\
\hline
Canisius College & CS-1 & C/C++ & 30\\
York College & CS-1 & C/C++ & 120\\
Knox College \#1 & CS-1 & Java & 23\\
University of Auckland & Programming for Engineers & C & 30\\
\hline
\end{tabular}
\caption{CloudCoder pilot studies.}
\label{tab:courses}
\end{table*}

>>>>

\usepackage{listings}
\usepackage{hyperref}
\usepackage{booktabs}

\renewcommand{\topfraction}{0.9}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.84}

@@

\begin{table*}
\centering
\begin{tabular}{llll}
\toprule
Institution & Course & Language & Enrollment\\
\midrule
Canisius College & CS-1 & C/C++ & 30\\
York College & CS-1 & C/C++ & 120\\
Knox College \#1 & CS-1 & Java & 23\\
University of Auckland & Programming for Engineers & C & 30\\
\bottomrule
\end{tabular}
\caption{CloudCoder pilot studies.}
\label{tab:courses}
\end{table*}
